Roster Review (Generic)

### 2019-06-14 rosterReview_generic.Rmd
Latest rosters, ohtani missing

rosters %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 2)) %>% 
  arrange(zar %>% desc) %>% 
  select(name_full, positions, type, zar) %>% 
  View()
```

@@

rosters_by_position %>% 
  select(team, manager, name_full, position, zar, pos_zar) %>% 
  View()

>>>>

rosters %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 2)) %>% 
  arrange(zar %>% desc) %>% 
  select(team, name_full, positions, type, zar) %>% 
  View()
```

@@

rosters_by_position %>% 
  select(team, manager, name_full, position, zar, pos_zar) %>% 
  # filter(position %in% c('SP','RP')) %>% 
  View()
